%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Lachaise Assignment
% LaTeX Template
% Version 1.0 (26/6/2018)
%
% This template originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Marion Lachaise & François Févotte
% Vel (vel@LaTeXTemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{article}

\input{structure.tex} % Include the file specifying the document structure and custom commands

%----------------------------------------------------------------------------------------
%	ASSIGNMENT INFORMATION
%----------------------------------------------------------------------------------------

\title{COMP9417: Machine Learning Project} % Title of the assignment

\author{z5113817} % Author name and email address

\date{University of New South Wales --- \today} % University, school and/or department name(s) and a date

%----------------------------------------------------------------------------------------

\begin{document}

\maketitle % Print the title

%----------------------------------------------------------------------------------------
%	Main Contents
%----------------------------------------------------------------------------------------

% TODO: All code for this project is available \href{https://github.com/william-coulter/NBA-Injury-Predictor}{here}.

\section*{Motivation}

In the 1984 NBA draft, Sam Bowie was drafted as the number 2 pick to the Trail Blazers.
It might be shocking to hear that Bowie was drafted one place \emph{above} the hall of fame superstar Michael Jordan.
This was because the Trail Blazers needed a new superstar "big man" to replace the Center they lossed the season before.
Bowie had an impressive 76 games with the Trail Blazers until a fracture in his left tibia put him out for the season.
Even though Bowie followed the recommened recovery time, the rest of Bowie's career was undermined by the recurring injury.
In 10 seasons with the NBA, Bowie only appears in 511 games.\\

The question is, even though injuries in sport and in the NBA can seem random, can a
machine learning model be used to eliminate some of the unpredictability and determine the likelihood 
that a player will suffer a major injury in the current season?

\section*{The Goal}

Create a model that assigns a likelihood that a player will \emph{suffer a major injury}
given their current performance. Suffering a major injury can be defined as a physical 
injury that leaves the player missing 15 or more games.

% TODO: A background on similar projects / how this project is unique?

\newpage

\section*{The Data}

\subsection*{Datasets}

The datasets were scraped from various sources such as 
\href{https://www.prosportstransactions.com/basketball}{prosporttransactions} and 
\href{https://www.basketball-reference.com/}{basketball-refrence}. The scrapers
were sourced from \textbf{elap733}'s repository found
\href{https://github.com/elap733/NBA-Injuries-Analysis/tree/master/src/d01_scrapes}{here}.\\

The following datasets can be found in the \textbf{data/raw} directory:
\begin{itemize}
    \item \textbf{player\_stats}: Contains every NBA player's basic statistics for a given season.
    \item \textbf{injury\_list}: Contains information on when players were acquired on and relinquished from NBA injury list.
    \item \textbf{missed\_games}: Contains information on games which players missed (not necessarily due to injury).
    \item \textbf{all\_games\_schedule}: The schedule for every NBA team.
\end{itemize}

The data ranges from 2010 to today.

\subsection*{Cleaning}

For the most part, the data contains pretty clean data with no missing entries
or gibberish values. The datasets were last scraped in 2019 however, so I had to 
do some additional scraping to obtain the latest data. Luckily, the scrapers 
still worked just fine.\\

For cleaning, all that I had to do was append the latest scraped data
with the existing datasets. The cleaned datasets can be viewed at \textbf{data/cleaned}.

\section*{Processing Data}

\subsection*{The Injury List}

The injury list in the NBA isn't quite as the name suggests. Rather than being a list
of players who are currently suffering from physical injury, players who miss games
for other reasons can be placed on this list. Other reasons include:

\begin{itemize}
    \item \textbf{illness}: TODO: obtain number of entries that satisfy this criteria.
    \item \textbf{COVID-19}
    \item \textbf{personal reasons}: e.g birth of child.
\end{itemize}

TODO: Make a new dataset from this (injury\_list\_cleaned)

For this project, I have defined a "major injury" as a physical injury that 
results in a player missing 15 or more games.

Additionally, the Injury List contains when a player was acquired on the injury list
as well as relinquished. TODO:

\subsection*{New Fields}

So now we have X entries where players were acquired on the injury list
and missed 15 or more games.
We want to tell a bigger story with these entries by adding some more data 
around this. 

We want to answer questions such as: How was the player performing before this injury? How intense
was their team's schedule? Had they suffered an injury prior to this?



In his sophomore year, Bowie had suffered a stress fracture in his left tibia. Even though he gave this 

\newpage
\section*{Exploratory Analysis}



\section*{Model Selection}

\section*{Model Evaluation}

\section*{Conclusion}

\end{document}
